Pillar 2 - Topic Modeling

### 2019-01-10 Pillar 2 - Topic Modeling.Rmd
Fine-tuning YALM
Fitting LDA model

---
title: "Pillar 2 - Topic Modeling"
output: github_document
---

@@

## Fitting Model

>>>>

---
title: "Pillar 2 - Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

@@

## Fitting Model
```{r}
d_overview_cast <- d_overview_stem %>%
  count(Code, word, sort = T) %>%
  cast_dtm(Code,word, n)
```

```{r}
LDA_10 <- LDA(d_overview_cast, k = 10, control = list(seed = 123))
LDA_17 <- LDA(d_overview_cast, k = 17, control = list(seed = 123))
LDA_25 <- LDA(d_overview_cast, k = 25, control = list(seed = 123))
```

## Results
